---
title: "hw3"
author: "Jiabei Wang"
date: "2018???10???11???"
output: html_document
---

```{r setup, include=FALSE}
library(p8105.datasets)
library(tidyverse)
data(brfss_smart2010)  
brfss_smart2010 = janitor::clean_names(brfss_smart2010) %>% 
filter(topic == "Overall Health") %>%
mutate(response = forcats::fct_relevel(response, c("Excellent", "Good", "Very good", "Fair", "Poor")))
year_2002 = filter(brfss_smart2010, year == 2002)%>%
group_by(locationdesc,locationabbr) %>% group_by(locationabbr) %>% summarize(n=n()/5) ##7 locations observed

year_2002_2010 = brfss_smart2010 %>%
group_by(locationdesc,locationabbr, year) %>% group_by(locationabbr, year) %>%
summarize(n=n()/5)

ggplot(year_2002_2010, aes(x = year, y = n, color = locationabbr)) + 
    geom_line() + 
    theme(legend.position = "bottom") ##spaghetti plot

brfss_smart2010 %>%
  janitor::clean_names() %>%
  spread(key = response, value = data_value)%>% 
  janitor::clean_names() %>%
filter(year == 2002|year == 2006|year == 2010, locationabbr == 'NY' ) %>%
group_by(year) %>%
  #na.omit() %>%
summarize(mean = mean(excellent, na.rm = TRUE), sd = sd(excellent, na.rm = TRUE)) %>%
 knitr::kable(digits = 1) 

```
States CT, FL, and NC
Florida is the outlier, and most states range from zero to fifteen, and they do not have big changes through the year.

##Question 2

```{r}
data(instacart) 
data_instacart = janitor::clean_names(instacart) %>% 
group_by(aisle) %>%
summarize(n = n()) %>%
filter(min_rank(desc(n)) < 2)

##make a histogram
instacart %>%
  ggplot( aes(x = aisle_id)) +
  geom_histogram()

##
one = instacart %>%
filter(aisle == "baking ingredients"|aisle == "dog food care"|aisle =="packaged vegetables fruits") %>%
group_by(aisle, product_name) %>%
 count() %>%
  group_by(aisle) %>% 
filter(min_rank(desc(n)) < 2) 
 knitr::kable(one) 

## table 
data(instacart) 
mean_hour_data = most = janitor::clean_names(instacart) %>% 
  filter(product_name == "Pink Lady Apples"|product_name =="Coffee Ice Cream") %>%
  group_by(product_name, order_dow) %>%
summarize(order_eachday = sum(order_number)) %>%
spread(key = order_dow, value = order_eachday) %>%
  group_by(product_name)
knitr::kable(mean_hour_data) 


```
The number of observations in data_instacart is `r dim(data_instacart)`
Fresh vegetables are the most items ordered from. 
The key variables of the data set are order number, order dow, product name,and aisle. 

```{r}
library(tidyverse)
data (ny_noaa) 
  ny_noaa = janitor::clean_names(ny_noaa) %>%
  group_by(id)  %>%
    ##units
rename(prcp_mm = prcp, snow_in = snow, tmax_F = tmax, tmin_F = tmin) %>%
separate(date, into = c("year", "month", "day"), sep = "-") 

ny_noaa %>% 
    group_by(snow_in) %>%
   count() %>%
    filter(min_rank(desc(n)) < 2)  
```
The most observed value of snowfall is zero, since the most of time in NY, there's no snowfall. 

```{r}
a = ny_noaa %>% 
    group_by(id, month) %>%
  filter(month == "01"|month == "07") %>%
   mutate(tmax_F = as.numeric(tmax_F, na.rm=TRUE)) %>%
  summarize(mean_tmax_F = mean(tmax_F)) %>% 
  na.omit(mean_tmax_F)

 ggplot(a, aes(x =id, y = mean_tmax_F)) + 
  geom_point(alpha = .5) +
  geom_smooth(se = FALSE) +
   facet_grid(~month)
 
 ##Make a two-panel plot showing the average max temperature
b = ny_noaa %>% 
  na.omit(tmin_F)%>%
  na.omit(tmin_F) %>%
  mutate(tmax_F = as.numeric(tmax_F, na.rm=TRUE)) %>%
   mutate(tmin_F = as.numeric(tmin_F, na.rm=TRUE)) 
  ggplot(b, aes(x = tmax_F, y = tmin_F)) + 
  geom_hex()
  
##Make a two-panel plot showing (i) tmax vs tmin for the full dataset (note that a scatterplot may not be the best option); and (ii) make a plot showing the distribution of snowfall values greater than 0 and less than 100 separately by year.
  c = ny_noaa %>% 
  na.omit(snow_in) %>%
  mutate(snowfall = as.numeric(snow_in, na.rm=TRUE)) %>%
  filter(snowfall>0,snowfall<100) 
  ggplot(c, aes(x = snowfall, fill = year)) + 
  geom_density()
  
```
The size of the data set is `r dim(ny_noaa)`
The key variables of the original data set are id,date, snow, tmax, and tmin. 
There are missing data in variable "prcp", "snow", "snwd", "tmax", and "tmin". Among these variables, "tmax" and "tmin" have the largest number of missing values.


```{r}
library(ggplot2)
library(patchwork)
ggplot(b, aes(x = tmax_F, y = tmin_F)) + 
  geom_hex() + ggplot(c, aes(x = snowfall, fill = year)) + 
  geom_density() 
```

(2)From the scatterplot, the mean max temperature of january is around zero F, and the mean max temperature of july is around 300F. No outlier is observed.  
3(i) From the plot on the left, the value of tmin and tmax occur most around zero.
(ii)
From the plot on the right, the density is largest when the value of snowfall is zero. Also, the density of snow fall is gerally decreasing with the increasing value snowfall.  


